---
title: "Uncertainty analysis with ERA5"
execute: 
  echo: false
  fig-width: 10
  fig-height: 7
format: 
  revealjs:
    self-contained: true
    
---

```{r}
#| label: setup
#| include: false

library(tidyverse)
library(stars)

sf_use_s2(F)

dir_data <- "/mnt/pers_disk_300/dif_era_cordex"

source(here::here("side_projs", "uncertainty_analysis", "0_output_vars.R")) 

land_pol <- 
  "/mnt/bucket_mine/misc_data/physical/ne_110m_land/" |> 
  st_read(quiet = T)

land_df <- 
  land_pol %>% 
  st_coordinates %>% 
  as_tibble %>% 
  mutate(L = paste0(L1, "_", L2))



fn_plot <- function(stars_obj, revv, tit, subtit){
  
  # stars_obj = s
  # revv = r
  # tit = d
  # subtit = dd
  
  
  stars_obj <- suppressMessages(stars_obj[land_pol])
  
  un <- 
    stars_obj |> 
    pull() |> 
    units::deparse_unit()
  
  tb <- 
    stars_obj |>
    units::drop_units() |> 
    merge(name = "stats") |> 
    setNames("value") |> 
    as_tibble()
  
  lim <- max(abs(quantile(tb$value, c(0.5, 0.95), na.rm = T)))
  
  ggplot() +
    geom_raster(data = tb, aes(lon, lat, fill = value)) + 
    geom_path(data = land_df, aes(X, Y, group = L), linewidth = 0.25) +
    colorspace::scale_fill_binned_diverging(na.value = "transparent",
                                            n.breaks = 9,
                                            guide = guide_colorsteps(barheight = 0.5,
                                                                     barwidth = 24,
                                                                     title.position = "left"),
                                            name = un,
                                            limits = c(-lim, lim),
                                            rev = revv
    ) +
    facet_wrap(~stats, ncol = 2,dir = "v") +
    coord_cartesian(ylim = c(-55, 75), xlim = c(-155, 160)) +
    theme(axis.title = element_blank(),
          legend.position = "bottom") +
    labs(title = tit,
         subtitle = subtit)
  
}






fn_main <- function(nm, delta = F, revv = F, wl = NA) {
  
  # nm <- output_vars[1]
  
  if (delta & !is.na(wl)) {
    
    print("ERROR: delta maps don't have warming levels")
    
  } else {
    
    if (!delta) {
      f <- str_glue("{dir_data}/era-cordex-dif_{str_replace_all(nm, '_', '-')}.nc")
    } else {
      f <- str_glue("{dir_data}/era-cordex-dif-delta_{str_replace_all(nm, '_', '-')}.nc")
    }
  
  
    s <- 
      read_ncdf(f) |> 
      suppressMessages()
    
    if(!is.na(wl)) {
      
      s <- 
        s |> 
        slice(wl, wl)
      
    }
  
    if (!delta & is.na(wl)){
      
      d <- "Difference: CORDEX - ERA5 [0.5° WL]"
      
    } else if (!delta & !is.na(wl)) {
      
      d <- str_glue("Difference: CORDEX - ERA5 [{c('0.5° WL', '1.0° WL')[wl]}]")
      
    } else if (delta) {
      
      d <- "Difference in change: CORDEX - ERA5 [1.0° - 0.5° WL]"
      
    }
    
  
    dd <- 
      nm |> 
      str_replace_all("_", " ") |>  
      str_to_sentence()
    
    if (!revv) {
      r <- F
    } else {
      r <- T
    }

    fn_plot(s, r, d, dd)
    
  }
  
}


```


- Maps show CORDEX - ERA differences
  - For heat maps, red (blue) means CORDEX runs hotter (cooler) than ERA5
  - For water maps, red (blue) means CORDEX runs drier (wetter) than ERA5
- Three difference maps per variable: 
  - 0.5° WL
  - 1.0° WL (not available for water maps)
  -  Change (i.e. deltas) (1.0° - 0.5°)


---

```{r}

fn_main(output_vars[1],
        wl = 1)

```

---

```{r}

fn_main(output_vars[1],
        wl = 2)

```

---


```{r}

fn_main(output_vars[1],
        delta = T)

```

---

```{r}

fn_main(output_vars[2],
        wl = 1)

```

---

```{r}

fn_main(output_vars[2],
        wl = 2)

```

---

```{r}

fn_main(output_vars[2],
        delta = T)

```

---


```{r}

fn_main(output_vars[3],
        wl = 1)

```

---

```{r}

fn_main(output_vars[3],
        wl = 2)

```

---

```{r}

fn_main(output_vars[3],
        delta = T)

```

---


```{r}

fn_main(output_vars[4],
        wl = 1)

```

---

```{r}

fn_main(output_vars[4],
        wl = 2)

```

---

```{r}

fn_main(output_vars[4],
        delta = T)

```

---


```{r}

fn_main(output_vars[5],
        wl = 1)

```

---

```{r}

fn_main(output_vars[5],
        wl = 2)

```

---

```{r}

fn_main(output_vars[5],
        delta = T)

```

---


```{r}

fn_main(output_vars[6],
        wl = 1)

```

---

```{r}

fn_main(output_vars[6],
        wl = 2)

```

---

```{r}

fn_main(output_vars[6],
        delta = T)

```

---


```{r}

fn_main(output_vars[7],
        wl = 1)

```

---

```{r}

fn_main(output_vars[7],
        wl = 2)

```

---

```{r}

fn_main(output_vars[7],
        delta = T)

```

---


```{r}

fn_main(output_vars[8],
        wl = 1)

```

---

```{r}

fn_main(output_vars[8],
        wl = 2)

```

---

```{r}

fn_main(output_vars[8],
        delta = T)

```

---


```{r}

fn_main(output_vars[9],
        wl = 1)

```

---

```{r}

fn_main(output_vars[9],
        wl = 2)

```

---

```{r}

fn_main(output_vars[9],
        delta = T)

```

---


```{r}

fn_main(output_vars[10],
        wl = 1)

```

---

```{r}

fn_main(output_vars[10],
        wl = 2)

```

---

```{r}

fn_main(output_vars[10],
        delta = T)

```

---

```{r}

fn_main(output_vars[11],
        wl = 1)

```

---

```{r}

fn_main(output_vars[11],
        wl = 2)

```

---

```{r}

fn_main(output_vars[11],
        delta = T)

```

---


```{r}

fn_main(output_vars[12],
        wl = 1)

```

---

```{r}

fn_main(output_vars[12],
        wl = 2)

```

---

```{r}

fn_main(output_vars[12],
        delta = T)

```

---


```{r}

fn_main(output_vars[13],
        wl = 1)

```

---

```{r}

fn_main(output_vars[13],
        wl = 2)

```

---

```{r}

fn_main(output_vars[13],
        delta = T)

```

---


```{r}

fn_main(output_vars[14],
        wl = 1)

```

---

```{r}

fn_main(output_vars[14],
        wl = 2)

```

---

```{r}

fn_main(output_vars[14],
        delta = T)

```

---


```{r}

fn_main(output_vars[15],
        wl = 1)

```

---

```{r}

fn_main(output_vars[15],
        wl = 2)

```

---

```{r}

fn_main(output_vars[15],
        delta = T)

```

---


```{r}

fn_main(output_vars[16],
        wl = 1)

```

---

```{r}

fn_main(output_vars[16],
        wl = 2)

```

---

```{r}

fn_main(output_vars[16],
        delta = T)

```



---

### `{r} str_to_sentence(str_replace_all(output_vars[17], "_", " "))`
- No maps: basically everywhere is zero

---

### `{r} str_to_sentence(str_replace_all(output_vars[18], "_", " "))`
- No maps: basically everywhere is zero


---

```{r}

fn_main(output_vars[19],
        wl = 1)

```

---

```{r}

fn_main(output_vars[19],
        wl = 2)

```

---

```{r}

fn_main(output_vars[19],
        delta = T)

```

---

```{r}

fn_main(output_vars[20], revv = T)

```

---

```{r}

fn_main(output_vars[20], revv = T, delta = T)

```

---

```{r}

fn_main(output_vars[21], revv = T)

```

---

```{r}

fn_main(output_vars[21], revv = T, delta = T)

```

---

```{r}

fn_main(output_vars[22], revv = T)

```

---

```{r}

fn_main(output_vars[22], revv = T, delta = T)

```

---

```{r}

fn_main(output_vars[23], revv = T)

```

---

```{r}

fn_main(output_vars[23], revv = T, delta = T)

```






